Figures and results for main manuscript

### 2020-12-07 analysis/reports/manuscript_main.Rmd
filtering report

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 > s0,
         s0 > 1,
         !singletons,
         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
    Dataset = ifelse(Dataset == "fia", "Forest Inventory and Analysis", Dataset),
        Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
        Dataset = ifelse(Dataset == "mcdb", "Mammal Community DB", Dataset),
        Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
        Dataset = ifelse(Dataset == "misc_abund", "Miscellaneous Abundance DB", Dataset))

@@

To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities.

>>>>

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
    Dataset = ifelse(Dataset == "fia", "Forest Inventory and Analysis", Dataset),
        Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
        Dataset = ifelse(Dataset == "mcdb", "Mammal Community DB", Dataset),
        Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
        Dataset = ifelse(Dataset == "misc_abund", "Miscellaneous Abundance DB", Dataset))

@@

To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities. See rov_metric.md.
